\documentclass[]{report}   % list options between brackets        
\usepackage{graphicx, listings, color, caption}      % list packages between braces
\graphicspath{ {Images/} }

% type user-defined commands here

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
 
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}

\begin{document}

\title{CAB420 Project Proposal \\ \large{Movie Rating Prediction}}   % type title between braces
\author{
	Jarrod Williams\\
	\texttt{n9722068}
	\and 
	Caleb Geizer\\
	\texttt{n9488243}
	\and
	Alex Barnier\\
	\texttt{}
	\and	
	Matthew Miller\\
	\texttt{n9342401}
}
\maketitle

\subsection*{Project Objective}
This project aims to train a machine learning model capable of estimating the rating that a user will give a selected movie based on both previous ratings that have given movies and ratings other uses have given. 
\\~\\
Using the given trained model it becomes possible to determine which movies the user is likely to enjoy, enabling the construction of a movie recommendation system.
\\~\\
The project objective is to determine with a reasonable accuracy ($>$80\%), the user's rating on a 5 star scale. Based on this rating the model should be able to determine which movies are suitable for recommendation to the user.
\subsection*{Data Sets}
The data set being used is the education Movielens data set from Grouplens. This data set contains 100000 ratings, 1300 tags, 9000 movies, and 700 users. At the time of download it had last been updated October 2016.

\subsection*{Timeline}
\begin{itemize}
  \item Monday 14th - Submit Project Proposal 
  \item Friday 18th - Introduction/Motivation, Related Words and Data added to report.
  \item Monday 21st - Methodology, Comparison added to report.
  \item Friday 25th - Conclusion written and report is finalised.
  \item Monday 28th - Presentation prepared and ready to go during the week.
\end{itemize}



\end{document}
